COG-ED Manuscript

### 2021-08-17 06_Paper/COG-ED/Manuscript.Rmd
Added data cleaning code

  # put relevant data into a dataframe

>>>>

  # create empty data frames for loops to feed into

  data_nback <- data.frame(subject = character(), level = double(), target = character(),
                           response = character(), correct = double(), rt = double())
  data_ED <- data.frame(subject = character(), step = double(), choice = character(),
                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())

  # put relevant data into a dataframes

  for (i in 1:length(datalist_nback)) {

    newdata <- data.frame(datalist_nback[[i]][["Participant"]], datalist_nback[[i]][["currentlevel"]],
                          datalist_nback[[i]][["Stimulus"]], datalist_nback[[i]][["trial_resp.keys"]],
                          datalist_nback[[i]][["trial_resp.corr"]], datalist_nback[[i]][["trial_resp.rt"]])
    colnames(newdata) <- names(data_nback)
    data_nback <- rbind(data_nback, newdata)
  }

  for (i in 1:length(datalist_ED)) {

    newdata <- data.frame(datalist_ED[[i]][["Participant"]][2:length(datalist_ED[[i]][["Participant"]])],
                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
    colnames(newdata) <- names(data_ED)
    data_ED <- rbind(data_ED, newdata)
  }

  # replace some columns with 'easy to work with' values

  # the target column will contain 1 for targets and 0 for all non-targets
  data_nback[data_nback == "Target"] <- 1
  data_nback[data_nback == "Pretarget"|data_nback == "Lure"|data_nback == "Distractor"] <- 0
  data_nback$target <- as.numeric(data_nback$target)
  # the response column will contain 1 for responses and 0 for all non-responses
  data_nback[data_nback == "left"|data_nback == "right"] <- 1
  data_nback[data_nback == "None"] <- 0
  data_nback$response <- as.numeric(data_nback$response)
  # the choice column will contain 1 for the left button and 2 for the right button
  data_ED[data_ED == "EDleftbutton"] <- 1
  data_ED[data_ED == "EDrightbutton"] <- 2
  data_ED$choice <- as.numeric(data_ED$choice)

  # since only the last choice of each comparison is relevant, we will keep only those rows

  data_ED <- data_ED[data_ED$step == 6,]
